---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  cache = TRUE
)
```
# One R Package a Day

Checking my assumption rOpenSci packages were picked relatively often by [the RLangPackage Twitter account](https://twitter.com/RLangPackage) (read [its creation story](https://stevenmortimer.com/one-r-package-a-day/)).

## Get RLangPackage's timeline

Cf https://rtweet.info/articles/auth.html

```{r timeline}
timeline <- rtweet::get_timeline("RLangPackage", n = 3200)
```

## Parse URLs

I'll keep only tweets with a single URL, that needs to be a GitHub URL (a few times the account answered tweets of other accounts and included URLs)

```{r urls}
urls <- timeline$urls_expanded_url[lengths(timeline$urls_expanded_url) == 1]
urls <- unlist(urls)
urls <- urls[grepl("github\\.com", urls)]
urls <- urltools::url_parse(urls)
urls <- dplyr::group_by(urls, path)
urls <- dplyr::mutate(urls, 
                      account = gsub("\\/.*", "", path), 
                      repo = gsub(".*\\/", "", path))
urls <- dplyr::ungroup(urls)

```

## THE ANSWER

Out of `r nrow(urls)` featured packages, `r sum(urls$account == "ropensci" | urls$account == "ropenscilabs")` (`sum(urls$account == "ropensci" | urls$account == "ropenscilabs")`) were rOpenSci packages. It's not a lot but...

```{r answer}
library("magrittr")
dplyr::count(urls, account, sort = TRUE) %>%
  dplyr::filter(n >= 2) %>%
  knitr::kable()
```

The ropensci GitHub organization is the most represented one! 